\documentclass{screenplay}

%% PORTADA
\title{The Woods}
\author{López Aguilar César A.}
\address{
2017630901\\
Computer Animation\\
}

\begin{document}

\coverpage

%% first act -> 45 seconds
%% second act ->  90 seconds
%% third act -> 45 seconds

\fadein

%%  FIRST ACT
\extslug[night]{road}
A policeman is driving through a road surrounded by a forest. There is no moon, so the only light visible is that from the car and the spare signals of the road. The policeman is Nathan Hills, a 45 year old man. He looks older than he should be. He appears to be tired. It is because the constant night patrols he has been doing for the last month, since the increase of reports of missing people. An unintelligible message is heard from the radio. Nathan tries to fix the signal, but is surprised by an abandoned truck in the middle of the road. \\
He stops the car and gets off. Walks to the truck. The passenger door is wide open. Nathan uses a flashlight to investigate the vehicle. There is a trail of blood that leads to the bushes. In that moment, a noise comes from the trees. 

\begin{dialogue}[Shouting]{nathan}
This is the police! Is there anybody there?
\end{dialogue}

There is no answer. The noise gets quite and the bushes stop moving. Nathan walks slowly entering the forest. 

%% SECOND ACT
Nathan walks through the woods, following a weird trail of dirt and mud. There are distant sounds that Nathan does not understand where they came from; neither he knows what those sounds could be. It sounded like wind, but also like voices, or more precisely, like laments. \\
As he enters deeper into the woods, the trees become closer and crooked, making difficult the pass. As he struggles with all the branches and vines, he glimpses what it looks like a dead animal. The creature it is not clearly visible, but it looks like a combination of mud, furr and blud. Nathan frees himself from the branches and enters a field with no trees, but instead, there are big roots everywhere in the ground and a path that goes beyond the darkness of the forest. \\
Nathan follows the path and, as he walks through it, he sees different kind of marks in the trees on the side of the path. They look like symbols. Nathan approaches one of the, and touches it, but he does not understand their meaning.




%%THIRD ACT


%% FINAL
\fadeout


\end{document}