\documentclass{screenplay}

%% PORTADA
\title{The Woods}
\author{López Aguilar César A.}
\address{
2017630901\\
Computer Animation\\
}

\begin{document}

\coverpage
\fadein

\extslug[night]{road}
A car is driving through an old road in the woods. Its a luxurious car from the 1950s. Inside the vehicle we see two man: Nathan and Buck. Both men wear long black coats and hats. Buck, who is in the passenger seat, looks older. He has a straight, serious face and brown hair. He is smoking. Nathan, has a more juvenile face and has black hair. An old song is heard from the radio. Nathan taps his fingers in the wheel at the beat of the song. Bruck does not appear to give attention to the music.

The car stops on the side of the road. The music gets quite.
\begin{dialogue}[Without looking]{Bruck}
You know what to do. Follow the path. You'll know when to stop.
\end{dialogue}

Nathan gets off the vehicle, gets off his coat and rolls up his sleeves.. He walks to the backside of the car and opens the trunk. He takes out a shovel and throws it in the ground. Then, with much effort, he takes out a big elongated bag, from the size of a man. He begins to drag the bag and the shovel trough a narrow path between the trees. Meanwhile, Bruck passes to the driver's seat. 

\extslug[night]{woods}
The light coming from the car gets dimer as Nathan continues entering in the woods. At some point, the only light is that of the full moon which breaks in the crooked branches of the trees. The bag is heavy, so he walks slowly. As he enters more and more in the woods, different types of clothes are visible in the mud of the ground. The clothes look rotted and appeared to be much older than the 1950s. In the mud a skeletal hand emerges from the ground.

Finally, Nathan arrives at a small extension where the trees form an irregular circle. There's several kinds of junk and it smells like dead animals. Nathan takes the shovel and begins to dig in the ground. We can see him digging heavily, but the camera slowly pans to one side of the circle of trees where there is a pile of wreaked old shovels.

When Nathan finishes digging, he takes the bag and throws it at the hole. But, as he pulls up the bag, a branch rips one side of it. At the moment in which the bags falls, Nathan sees that there is no body in there, but just a dead deer.

\begin{dialogue}{Nathan}
    Oh, shit!
\end{dialogue}

Nathan shows terror before the revelation. He walks backwards slowly and we can see at the the distance multiple human-like  figures emerging from the ground and walking towards him.

Cut back to Buck. He hears distant screams. Then he throws his cigar through the window and turns on the engine. The music continues playing and Buck leaves with the car.


%% FINAL
\fadeout


\end{document}